\subsection{State of the Art}
We looked into the state of the art of scheduling software and found that 
Syllabus Plus, a product developed by Scientia, is used by a large number 
of colleges and universities around the world, including the University of 
Groningen~\cite{SyllabusPlus}. Syllabus Plus is described as an artificial 
intelligence solution, with its implementation resembling a constraint 
satisfaction problem solver. The program operates by collecting available 
data, which consists of foundation and student data. The former contains 
non-dynamic information about teacher staff and locations, while the latter 
involves dynamic data, such as student enrolments and course requirements. 
After a refinement phase for all data is performed, the program iterates 
through constraint reduction cycles, in which the hard constraints, soft 
constraints, rules and preferences are adjusted to some degree, until the 
stop criteria of the program are reached. The result is a working schedule 
that satisfies the target constraints.

The state of the art for using argumentation in the scheduling process is 
described in a paper by~\cite{Kuo:jc}. Here, a course-scheduling 
negotiating system is presented in which agents, who are representing 
teachers, are involved in the scheduling process. This involvement consists 
of negotiating and arguing with other agents, in order to reach a consensus 
about a particular room allocation or to change an agent's belief. Apart 
from beliefs, agents also posses individual preferences, to which a number 
of proposals are generated for every agent during the proposal generator 
phase of the algorithm. Proposals are abstract, but can for example take 
the form of agent A claiming room 1 for course X on time slot I. 

Next, during the negotiation process, every agent selects its most 
effective proposal out of the total list, by calculating an utility value 
for all proposals and selecting the best scoring option. The utility value 
is based on particular preferences for issues belonging to a given 
proposal. Every agent will then present their favourite proposal and will 
try to negotiate with other agents in order to reach a consensus about a 
single proposal. If such a consensus is indeed reached, the scheduling 
process is completed for the rooms, courses and agents involved in the 
proposal. If however no consensus is reached, the agent with the lowest 
so-called risk value is selected to concede. This risk value is evaluated for 
every agent by taking the utility value of the proposal chosen by the agent 
minus the maximal cost of conceding ones own proposal in favour of that of 
another. If there are no more proposals to be selected that have not been 
used during the negotiation process this round, the argumentation process 
is started. Else, the conceding agent is prompted to select an available 
proposal and resume the negotiation process. 

In the argumentation process, the conceding agent chooses the agent with 
the lowest risk value (itself excluded) to argue with. The two agents will
then look for conflicting issues between them. If such issues exist, both
agents will create arguments based on their beliefs and will try to
persuade each other through their arguments and counterarguments. The agent
that at some point fails to defend himself is prompted to evolve its belief
on a particular issue, after which a new negotiation process is started
again. The conceding agent will try to look for other agents if no
conflicting issues are found, until no more agents are available to argue
with. In that case, a new negotiation process is started. The entire
scheduling process will continue until a consensus is reached during a
negotiation phase.

The issue with this approach is that this will not lead to a perfect
schedule, since the agents do not have perfect information, without having
the added benefit of the explanatory power that an argumentative approach
could have. And if the agents would have perfect information, then it
basically boils down to solving a constraint satisfaction problem, which
leaves us back at the older solution to scheduling. We hope to give an
approach that will give us this explanation, that leads to a clear conflict
free schedule and does not require prefect information for all the separate
agents.
